\mireval{}

### 2014-05-08 paper/paper.tex
Slightly more vague but more correct description of what MATLAB is doing.  It's not possible to explain it exactly without a lot of space.

The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first and last bins are 1/2 of the width of the rest of the bins.
It also uses one more bin than is specified by the user.
\mireval{} uses a standard uniformly-binned histogram with as many bins as are specified by the user.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.

>>>>

The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.
